Constraint Programming - Inside Gecode

### 2014-05-06 paper.tex
corrections Michael

	\subsubsection{Depth-First Search with Optimization}
	If in the constraint programming a objective is defined which should be either minimized or maximized a modified version of the Depth-first search can be applied. The only difference is that it evalutes the objective function for every found solution concerning the constraints and stores during the search only the best one. To accelerate the search it is possible to add an additional constraint which defines that the new objective must better than the best so far. Through this enhancement even more sub trees are pruned and the search is faster.

@@

	\subsubsection{Branch-and-Bound Search}
	Branch-and-bound refers actually to two parts, a Branch-and-reduce search and bounding. Branch-and-reduce itself is the continous constraint propagation to reduce the variable domains combined with branching when there is no further reduction by constraint propagation possible. A simple heuristic for branching would be to split the biggest domain into two equal sized intervals.

	Bounding is then the part which transforms the Branch-and-reduce search into an optimization. To be able to do this an objective function is necessary. In the following I will assume that the objective function has to be minimized without a loss of generality.

@@

	\subsubsection{Limited Discrepancy Search}
	Limited Discrepancy Search falls into the category of Best-first searches and was first mentioned by Harvey and Ginsberg in \cite{limitedDiscrepancy}. It depends on some heurisitics for the tree, which are determined through branching strategies. The basic concept is that during a chronological backtrack search a wrong turn close to the root is first of all very expensive and second heurisitics work worse the farther away from the solution, therefore closer to the root, they are. Consequently, in a chronological backtrack search the worst decisions are the most expensive ones. The Limited Discrepancy Search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement compared to a chronological backtrack was shown by experimental results and theoretical proven in \cite{limitedDiscrepancy}.

@@

	\section{Conclusion}
	Constraint programming is a very useful tool in practice, as it can solve abritrary combinatorial or optimization problems. \emph{Gecode}, as representant of the various toolsets, implements a very handy interface to transform a mathematical description of a problem into code, which then can be used to solve the problem. In conclusion, \emph{Gecode} provides all the necessary tools, combines them with a nice interface, and is still very flexible concering optimzation for a certain area through the possibility to implement custom search strategies, based on some well studied and efficient algorithms.

>>>>

	\subsubsection{Depth-First Search with Optimization}
	If in the constraint programming an objective is defined which should be either minimized or maximized a modified version of the Depth-first search can be applied. The only difference is that it evalutes the objective function for every found solution concerning the constraints and stores during the search only the best one. To accelerate the search it is possible to add an additional constraint which defines that the new objective must better than the best so far. Through this enhancement even more sub trees are pruned and the search is faster.

@@

	\subsubsection{Branch-and-Bound Search}
	Branch-and-bound refers actually to two parts, a Branch-and-reduce search and bounding. If there is no further reduction of variable domains possible the step of Branch-and-reduce can be applied, which means applying a branching strategy to split the search space into two disjoints sets. One example for a heuristic for branching would be to split the biggest domain into two equal sized intervals.

	Bounding is then the part which transforms the Branch-and-reduce search into an optimization. To be able to do this an objective function is necessary. In the following discussion on bounding I will assume that the objective function has to be minimized without a loss of generality.

@@

	\subsubsection{Limited Discrepancy Search}
	Limited Discrepancy Search falls into the category of Best-first searches and was first mentioned by Harvey and Ginsberg in \cite{limitedDiscrepancy}. It depends on some heurisitics for the tree, which are determined through branching strategies. The basic concept is that during a chronological backtrack search a wrong turn close to the root is first of all very expensive. Second, heuristics work worse the farther away from the solution they are applied, therefore decisions close to the root node are possible to fail. Consequently, in a chronological backtrack search the worst decisions are the most expensive ones. The Limited Discrepancy Search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement compared to a chronological backtrack was shown by experimental results and theoretical proven in \cite{limitedDiscrepancy}.

@@

	\section{Conclusion}
	Constraint programming is a very useful tool in practice, as it can solve abritrary combinatorial or optimization problems. \emph{Gecode}, as representant of the various toolsets, implements a handy interface to transform a mathematical description of a problem into code, which then can be used to solve the problem. In conclusion, \emph{Gecode} provides all the necessary tools, combines them with a nice interface, and is still very flexible concering optimzation for a certain area through the possibility to implement custom search strategies, based on some well studied and efficient algorithms.
